On Misuses of the Kolmogorov–-Smirnov Test for One Sample Goodness-of-Fit

### 2022-04-27 Manuscript/manuscript.tex
edits to introduction

\jy{keep line width under 80 characters in tex source}

@@

The Kolmogorov-Smirnov (KS) statistic is one of the most popular goodness-of-fit 
tests for comparing a sample with a hypothesized parametric distribution.
Let $X_1, ..., X_n$ be a random sample from some continuous
distribution. The null hypothesis $H_0$ is that the population distribution is $F$.
Let $F_n(\cdot)$ be the empirical cumulative distribution. The KS statistic is
\[
  D = \sup_x {\lvert F_{n}(x) - F(x) \rvert}.
\]
\jy{use upper case for random variables}
The distribution of $D$ under $H_0$ turned out to be independent of the
distribution $F$ and  table of critical values for $D$ has been constructed
\citet{Massey} for various sample sizes $n$ and significance 
levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical value, 
the null hypothesis is rejected. The KS test is available in popular statistical
software packages, such as function \texttt{ks.test} in R \citep{R}.
\jy{cite R and also some of the references on the help page of the function}

The standard one-sample KS test applies to independent data with a continuous
hypothesized distribution that is completely specified.
\jy{this paragraph needs some reorganization.
  Flow: not applicable to discrete or rounded data (give references; which is
  not the focus of this paper);
  not applicable to fitted distributions;
  not applicable to serially dependent data}
\jy{break the big paragraph into smaller ones}
Often in literature, it has been "discovered" that the test loses its power when 
applied to dependent or discrete data with hypothesized distributions containing 
estimated parameters. In the case of estimated parameters, \citet{Steinskog} 
demonstrates the change in power when using estimated parameters and stress caution in 
using the KS test in such ways. \citet{Lilliefors} shows 
that using the standard table when values of the mean and standard deviation are 
estimated obtains extremely conservative results. This is supported by \citet{Capasso}, which 
concludes that failing to re-estimate the parameters may lead to wrong, overly-conservative 
approximations to the distributions of goodness-of-fit test statistics based on the empirical 
distribution function. \citet{Capasso} also notes that the impact of this possible mistake 
may turn out to be dramatic and does not vanish as the sample size increases. Remedies are provided 
by \citet{Genest} and \citet{Babu} in the form of bootstrap. \citet{Genest} provides validity 
for using parametric bootstrap with various goodness-of-fit tests. \citet{Babu} details 
the bootstrap procedure for goodness-of-fit tests and notes that both parametric and 
non-parametric procedures lead to correct asymptotic levels, however there is a correction 
required for the non-parametric case. In the case of dependent data, \citet{Durilleul} demonstrates
that the KS statistic is too liberal for medium-to-high positive autocorrelation values. 
\citet{Durilleul} also shows that for negative autocorrelation values, the behavior is 
asymmetrical with respect to positive values. For remedies, \citet{Weiss} provides a 
procedure that is applicable specifically for data modeled by the second-order auto-regressive (AR) 
process where the parameters are known. \citet{Lanzante} tests various strategies for dealing with 
temporal dependence and concludes that a test based on Monte-Carlo simulations performed the best.
We propose a bootstrap procedure involving copulas to account for dependence.

The contribution of this paper is a demonstration of misuses of the one-sample
KS test in three scenarios and their remedies in practice. In order to set 
up the demonstrations, simulated data is used throughout. Unless otherwise specified, 
the random data is generated from a standard normal distribution with sample size $n = 100$. 
Therefore the cumulative distribution $F(x)$ of the KS test for much of this paper is standard normal.
\jy{Let's not restrict to normal distributions.}

The rest of the paper is organized as follows. Section~\ref{sec:fitted}
investigates the scenario where the hypothesized distribution has an unspecified
parameters. Both parametric and nonparametric bootstrap are available to fix the
issue. Section~\ref{sec:dependence} ... ... \jy{fill this}
Section~\ref{sec:conclusion} concludes with a discussion.

>>>>

@@

The Kolmogorov-Smirnov (KS) statistic is one of the most popular goodness-of-fit 
tests for comparing a sample with a hypothesized parametric distribution.
Let $X_1, ..., X_n$ be a random sample from some continuous distribution. 
The null hypothesis $H_0$ is that the population distribution is $F$.
Let $F_n(\cdot)$ be the empirical cumulative distribution. The KS statistic is
\[
  D = \sup_x {\lvert F_{n}(x) - F(x) \rvert}.
\]
The distribution of $D$ under $H_0$ turned out to be independent of the
distribution $F$ and a table of critical values for $D$ has been constructed
\citet{Massey} for various sample sizes $n$ and significance 
levels $\alpha$. If the value of $d$ exceeds the test's corresponding critical 
value, the null hypothesis is rejected. The KS test is available in popular 
statistical software packages, such as function \texttt{ks.test} in R 
\citep{R, Marsaglia}.

The standard one-sample KS test applies to independent data with a continuous
hypothesized distribution that is completely specified.
\jy{this paragraph needs some reorganization.
  Flow: not applicable to discrete or rounded data (give references; which is
  not the focus of this paper);
  not applicable to fitted distributions;
  not applicable to serially dependent data}
\jy{break the big paragraph into smaller ones}
Often in literature, it has been "discovered" that the test loses its power when 
applied to dependent or discrete data with hypothesized distributions containing 
estimated parameters. DISCRETE SECTION HERE. This issue with discrete or rounded
is not the focus of this paper, though is a common misuse that should be 
noted.

The KS test is not applicable when the hypothesized distribution contains fitted
parameters. \citet{Steinskog} demonstrates the change in power when using 
estimated parameters and stress caution in using the KS test in such ways. 
\citet{Lilliefors} shows that using the standard table when values of the mean 
and standard deviation are estimated obtains extremely conservative results. 
This is supported by \citet{Capasso}, which concludes that failing to 
re-estimate the parameters may lead to wrong, overly-conservative approximations 
to the distributions of goodness-of-fit test statistics based on the empirical 
distribution function. \citet{Capasso} also notes that the impact of this 
possible mistake may turn out to be dramatic and does not vanish as the sample 
size increases. Remedies are provided by \citet{Genest} and \citet{Babu} in the 
form of bootstrap. \citet{Genest} provides validity for using parametric 
bootstrap with various goodness-of-fit tests. \citet{Babu} details the bootstrap
procedure for goodness-of-fit tests and notes that both parametric and 
non-parametric procedures lead to correct asymptotic levels, however there 
is a correction required for the non-parametric case.

In the case of serially dependent data, \citet{Durilleul} demonstrates that the 
KS statistic is too liberal for medium-to-high positive autocorrelation values. 
\citet{Durilleul} also shows that for negative autocorrelation values, the 
behavior is asymmetrical with respect to positive values. For remedies, 
\citet{Weiss} provides a procedure that is applicable specifically for data 
modeled by the second-order auto-regressive (AR) process where the parameters 
are known. \citet{Lanzante} tests various strategies for dealing with temporal 
dependence and concludes that a test based on Monte-Carlo simulations performed 
the best. We propose a parametric bootstrap procedure involving copulas to 
account for dependence.

The contribution of this paper is a demonstration of misuses of the one-sample
KS test in three scenarios and their remedies in practice. In order to set 
up the demonstrations, simulated data is used throughout. The random data is 
generated with sample size $n = 100$ and the remedies are performed on various
families of distributions.

The rest of the paper is organized as follows. Section~\ref{sec:fitted}
investigates the scenario where the hypothesized distribution has unspecified
parameters. Both parametric and nonparametric bootstrap are available to fix the
issue. Section~\ref{sec:dependence} investigates the scenario where the data of 
the empirical distribution is serially dependent. Our bootstrap procedure 
employing copulas is a working solution. Section~\ref{sec:fittedwithdependence}
explores the case where a combination of the first two scenarios occurs. The 
copula procedure is available as a fix here as well. 
Section~\ref{sec:conclusion} concludes with a discussion.
